=enter title here=

### 2025-05-27 ms/ms.tex
Updates from Overleaf

Though ESMs show a slight increase in spring precipitation in the region, there does not seem to be an attributable influence of climate change on NAM precipitation. Previous work indicates that the 2020 SWUS drought was not exacerbated by climate change, but was rather a result of  internal atmospheric variability \cite{seager2022}.

@@

%\bibliography{ enter your bibtex bibliography filename here }

>>>>

Though ESMs show a potential reduction in spring precipitation in the region, there does not seem to be an attributable influence of climate change on NAM precipitation. Previous work indicates that the 2020 SWUS drought was not exacerbated by climate change, but was rather a result of  internal atmospheric variability \cite{seager2022}.

@@

\bibliography{ms/refs}
